Propositions as Sessions, Mechanically

### 2015-04-23 paper/presentation.tex
Added more slides and figures (emulating my paper presentation).

\begin{frame}[fragile]
\oldframetitle{CP Rules: Formal vs. Informal Comparison}
\begin{tabular}{lc}
\begin{coqp}
Inductive cp_rule : proc -> penv -> Prop :=
  | $\cdots$
  | cp_cut :
      forall (L:atoms) P Q A $\Gamma$ $\Delta$P $\Delta$Q
             (PER: Permutation $\Gamma$ ($\Delta$P ++ $\Delta$Q))
             (CPP: forall (x:atom) (NL: x $\notin$ L),
                     (open_proc P x) $\tpcp$ (x $\sim$ A) ++ $\Delta$P)
             (CPQ: forall (x:atom) (NL: x $\notin$ L),
                (open_proc Q x) $\tpcp$ (x $\sim$ $\dualbt{A}$) ++ $\Delta$Q),
        $\nu$ A.(P $\mid$ Q) $\tpcp$ $\Gamma$
  | $\cdots$
\end{coqp} &
\begin{math}
\colored
\inference{
  \tm{P} \tpvdash \tp{\Gamma \comma \tmof{x}A}
  &
  \tm{Q} \tpvdash \tp{\Delta \comma \tmof{x}\dualbt{A}}
}{}{
  \tm{\nu x \of{A}.(P \mid Q)} \tpvdash \tp{\Gamma \comma \Delta}
}
\end{math}
\end{tabular}

%% \begin{coqp}
%% Inductive cp_rule : proc -> penv -> Prop :=
%%   | $\cdots$
%%   | cp_cut :
%%       forall (L:atoms) P Q A $\Gamma$ $\Delta$P $\Delta$Q
%%              (PER: Permutation $\Gamma$ ($\Delta$P ++ $\Delta$Q))
%%              (CPP: forall (x:atom) (NL: x $\notin$ L),
%%                      (open_proc P x) $\tpcp$ (x $\sim$ A) ++ $\Delta$P)
%%              (CPQ: forall (x:atom) (NL: x $\notin$ L),
%%                 (open_proc Q x) $\tpcp$ (x $\sim$ $\dualbt{A}$) ++ $\Delta$Q),
%%         $\nu$ A.(P $\mid$ Q) $\tpcp$ $\Gamma$
%%   | $\cdots$
%% \end{coqp}
\end{frame}

\begin{comment}
lets take a look at cp's typing rules. here we used a well typed relation on
the process terms of cp. we require additional assumptions for environment
ordering and more attention is paid to the opening of subprocesses. this
presents the informal and formal definitions of cut. There is no overhead when
introducing binders to the subprocesses or for environment ordering, but apart
from these representation issues the rules look similar which could assist the
uptake of such formal tools by programming language researchers.
\end{comment}

@@

\begin{frame}
\oldframetitle{Subject Reduction in CP}
\subred
\begin{itemize}
\item {\fontsize{6}{7.2}\selectfont blah one}
\item blah two
\item blah three
\item blah four
\item blah five
\item blah six
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Subject Reduction in CP}
\[\colored
\begin{array}{c}
\mbox{Subject reduction} = \left\{ \begin{array}{ll}
                                   \mbox{Principal cut reductions}~(\beta)\\
                                   \mbox{Commuting Conversions}~(\kappa)
                                   \end{array} \right.
\\~\\
(\kappa_{\otimes1}) \quad
\tm{\nu z\Of{C}.(x[y].(P \mid Q) \mid R)}
\quad \becomes \hfill
\hfill \tm{x[y].(\nu z\Of{C}.(P \mid R) \mid Q)}
\end{array}
\]
\end{frame}

@@

>>>>

\begin{frame}[fragile]
\oldframetitle{CP Rules: Formal vs. Informal Comparison}
\begin{tabular}{lc}
\begin{coqp}
Inductive cp_rule : proc -> penv -> Prop :=
  | $\cdots$
  | cp_cut :
      forall (L:atoms) P Q A $\Gamma$ $\Delta$P $\Delta$Q
             (PER: Permutation $\Gamma$ ($\Delta$P ++ $\Delta$Q))
             (CPP: forall (x:atom) (NL: x $\notin$ L),
                     (open_proc P x) $\tpcp$ (x $\sim$ A) ++ $\Delta$P)
             (CPQ: forall (x:atom) (NL: x $\notin$ L),
                (open_proc Q x) $\tpcp$ (x $\sim$ $\dualbt{A}$) ++ $\Delta$Q),
        $\nu$ A.(P $\mid$ Q) $\tpcp$ $\Gamma$
  | $\cdots$
\end{coqp} &
\begin{math}
\colored
\inference{
  \tm{P} \tpvdash \tp{\Gamma \comma \tmof{x}A}
  &
  \tm{Q} \tpvdash \tp{\Delta \comma \tmof{x}\dualbt{A}}
}{}{
  \tm{\nu x \of{A}.(P \mid Q)} \tpvdash \tp{\Gamma \comma \Delta}
}
\end{math}
\end{tabular}
\end{frame}

\begin{comment}
CP rules were encoded as an inductive in Coq and an example for cut is shown
here. CP provided challenges for metatheory library since it differ in many
respects to lambda calculi. for example, in the lambda calculus one does not
work up to permutation of binders whereas in a process calculus these kinds of
structural equivalences are standard. we require additional assumptions for
environment ordering and more attention is paid to the opening of
subprocesses. metatheory did not support permutations and as a result of this
work some basic operations and custom tactics were developed. the custom
tactics can solve simple permutation goals via simple proof search. this slide
presents the informal and formal definitions of cut. There is no overhead when
introducing binders to the subprocesses or for environment ordering, but apart
from these representation issues the rules look similar which could assist the
uptake of such formal tools by programming language researchers.
\end{comment}

@@

\begin{frame}[fragile]
\oldframetitle{Subject Reduction in CP}
\begin{tabular}{ll}
\begin{coq}
Theorem proc_sub_red:
  forall $\Gamma$ P Q
         (WT: P $\tpvdash_{cp}$ $\Gamma$)
         (RED: P $\becomes$ Q),
    Q $\tpvdash_{cp}$ $\Gamma$.
\end{coq} &
\begin{math}
\becomes \defeq \left\{ \begin{array}{ll}
                   \mbox{Principal cut reductions}~(\beta)\\
                   \mbox{Commuting Conversions}~(\kappa)
                   \end{array} \right.
\end{math}
\end{tabular}
\begin{itemize}
\item {\fontsize{6}{7.2}\selectfont blah one}
\item blah two
\item blah three
\item blah four
\item blah five
\item blah six
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
\oldframetitle{Principal Cut Reduction ($\beta_{!?}$)}
\begin{tabular}{c}
\begin{coq}
Lemma reduce_spawn:
  forall P Q A dA $\Gamma$
         (DUA: dual_props A dA)
         (WT: $\nu$ !A.(!0(A).P $\mid$ ?0[dA].Q) $\tpcp$ $\Gamma$),
    $\nu$ A.(P $\mid$ Q) $\tpcp$ $\Gamma$.
\end{coq}
\\~\\
\begin{math}
\begin{array}{c}
\small
\colored
\inference{
  \inference{
    \tm{P} \tpvdash \tp{{?\Gamma} \comma \tmof{y}A}
  }{!}{
    \tm{!x(y).P} \tpvdash \tp{{?\Gamma} \comma \tmof{x}{!A}}
  }
  &
  \inference{
    \tm{Q} \tpvdash \tp{\Delta \comma \tmof{y}\dualbt{A}}
  }{?}{
    \tm{?x[y].Q} \tpvdash \tp{\Delta \comma \tmof{x}{?\dualbt{A}}}
  }
}{}{
  \tm{\nu x \Of{!A}.(!x(y).P \mid {?x[y].Q})} \tpvdash
    \tp{{?\Gamma} \comma \Delta}
}
\becomes
\inference{
  \tm{P} \tpvdash \tp{{?\Gamma} \comma \tmof{y}A}
  \\
  \tm{Q} \tpvdash \tp{\Delta \comma \tmof{y}\dualbt{A}}
}{}{
  \tm{\nu y\Of{A}.(P \mid Q)} \tpvdash \tp{{?\Gamma} \comma \Delta}
}
\normalsize
\end{array}
\end{math}
\end{tabular}
\end{frame}

\begin{frame}
\[\colored
\begin{array}{c}
(\beta_{!?}) \quad
\tm{\nu x \Of{!A}.(!x(y).P \mid {?x[y].Q})}
\quad \becomes \quad
\tm{\nu y\Of{A}.(P \mid Q)}
\\~\\
(\kappa_{\otimes1}) \quad
\tm{\nu z\Of{C}.(x[y].(P \mid Q) \mid R)}
\quad \becomes \quad
\tm{x[y].(\nu z\Of{C}.(P \mid R) \mid Q)}
\end{array}
\]
\end{frame}
